Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-06 WSSSPE1_report/WSSSPE1_summary_report.tex
Moving Career Track subsection under Cross-cutting issues.
Also adjusts section level, label, and refs for/to Defining Sustainability.

Bourne's keynote presentation was entitled ``A Recipe for Sustainable
Software,'' and developed based on his experiences.  He emphasized that
sustainability for software ``does not just mean more money from
Government'' (see also Section~\ref{sec:cross-cutting}).  Other
factors to consider, he mentioned, include costs of production, ease
of maintenance, community involvement, and distribution channels.

@@

The question of what ``sustainable'' means in the context of software was
raised (see \S\ref{sec:cross-cutting}.) The resources at \url{http://oss-watch.ac.uk/resources/ssmm} discuss what
to look for when choosing software for procurement, or reuse in further software
development. Regardless of the license and development model that will be used,
the future of the project must be considered. Even if a particular piece of
software satisfies today's requirements, will it continue to do so in the
future? Important questions include whether the supplier will still be around in five
years time, will it still care for its customers needs, will it be responsive to
bug reports and feature requests? Should you tie your investment to a single
supplier using a proprietary product, or ensure the project uses an OSI-approved
license, and can outlive any single entity if the software is still important.

@@

The workshop submissions grouped under this section provide frameworks
for thinking about, researching and understanding which elements of sustainability
are important and how they relate. Although there is substantial
overlap between the frameworks, they have different emphases and
extents.  Each paper in this group included a definition of sustainability,
with many overlaps.  In essence the papers related the question to
change over time, an idea well captured in the definition used by the
UK's Scientific Software Sustainability Institute: ``software you use
today will be available---and continue to be improved and
supported---in the future,'' as quoted in~\cite{Venters_WSSSPE}. This
idea was also expressed as software that continues to serve its
users~\cite{Pierce_WSSSPE}.  A more thorough discussion of definitions
of software sustainability is presented in \S\ref{sec:cross-cutting}.

@@

\subsection{Career Tracks for Scientific Software Developers}

@@

\section{Cross-cutting Issue: Defining Sustainability \note{lead: Daniel S. Katz}}  \label{sec:cross-cutting}

@@

>>>>

Bourne's keynote presentation was entitled ``A Recipe for Sustainable
Software,'' and developed based on his experiences.  He emphasized that
sustainability for software ``does not just mean more money from
Government'' (see also Section~\ref{sec:defining-sustainability}).  Other
factors to consider, he mentioned, include costs of production, ease
of maintenance, community involvement, and distribution channels.

@@

The question of what ``sustainable'' means in the context of software was
raised (see \S\ref{sec:defining-sustainability}.) The resources at \url{http://oss-watch.ac.uk/resources/ssmm} discuss what
to look for when choosing software for procurement, or reuse in further software
development. Regardless of the license and development model that will be used,
the future of the project must be considered. Even if a particular piece of
software satisfies today's requirements, will it continue to do so in the
future? Important questions include whether the supplier will still be around in five
years time, will it still care for its customers needs, will it be responsive to
bug reports and feature requests? Should you tie your investment to a single
supplier using a proprietary product, or ensure the project uses an OSI-approved
license, and can outlive any single entity if the software is still important.

@@

The workshop submissions grouped under this section provide frameworks
for thinking about, researching and understanding which elements of sustainability
are important and how they relate. Although there is substantial
overlap between the frameworks, they have different emphases and
extents.  Each paper in this group included a definition of sustainability,
with many overlaps.  In essence the papers related the question to
change over time, an idea well captured in the definition used by the
UK's Scientific Software Sustainability Institute: ``software you use
today will be available---and continue to be improved and
supported---in the future,'' as quoted in~\cite{Venters_WSSSPE}. This
idea was also expressed as software that continues to serve its
users~\cite{Pierce_WSSSPE}.  A more thorough discussion of definitions
of software sustainability is presented in \S\ref{sec:defining-sustainability}.

@@

@@

\section{Cross-cutting Issues} \label{sec:cross-cutting}

\subsection{Defining Sustainability \note{lead: Daniel S. Katz}}  \label{sec:defining-sustainability}

@@

\subsection{Career Tracks for Scientific Software Developers} \label{sec:career-tracks}
